BACI of biomass change for VOCC source cells for all years

### 2019-09-30 analysis/VOCC/4-vocc-BACI-multiyear.Rmd
remove global_only as all models now global

#### Set default cell sizes and scale
```{r, echo=FALSE}
global_only <- TRUE
input_cell_size <- 2
dist_intercept <- input_cell_size/2
scale_fac <- 1
delta_t_step <- 2
skip_time <- NULL
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
if (region == "both odd year surveys") {
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  start_years <- list("2009"=2009, "2011"=2011, "2013"=2013, "2015"=2015) 
  # maybe remove 2011 & 2015 once we can add "2017"=2017 to avoid start and end values overlapping
  years <- NULL
}

if (region == "West Coast Vancouver Island") {
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")
  start_years <- list("2008"=2008, "2010"=2010, "2012"=2012, "2014"=2014, "2016"=2016) 
  # prob need to remove 2010 & 2014
  years <- NULL
}

if (region == "West Coast Haida Gwaii") {
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  start_years <- list("2008"=2008, "2010"=2010, "2012"=2012, "2014"=2014, "2016"=2016) 
  # prob need to remove 2010 & 2014
  years <- NULL
}
```

@@

if (global_only) {
 root_params <- root_params %>% mutate(global = ifelse(grepl("_", model), "F", "T"))
 root_params <- filter(root_params, global == "T")
} else {
 if (model_ssid == 4) {
   root_params <- root_params %>% mutate(survey4 = ifelse(grepl("4", model), "T", "F"))
   root_params <- filter(root_params, survey4 == "T")
 }
}

if (climate == "temperature") {

temp_threshold <- params$threshold

@@

  upper_thresholds <- round(.upper[1], digits = 2)
   if (is.na(upper_thresholds)) {stop(print("Temp maximum not modelled"))}

@@

  .lower <- na.omit(.lower)
  lower_thresholds <- round(.lower[1], digits = 2)
  if (is.na(lower_thresholds)) {stop(print("DO minimum not modelled"))}
  lower_model <- root_params[rev(order(root_params$do_maxy)), ]$model

@@

# Calculate climate vectors
```{r}
vocc_by_year <- lapply(start_years, function(start_time) {

try({
  vocc <- readRDS(paste0(
    "data/vocc-", ssid_string, "-", climate_string, "-",
    min_string, "to", max_string, "-", start_time, "-", delta_t_total, ".rds"
  ))
})

@@

### Filter vectors to match optimal range for chosen species
```{r}
trimmed_vectors <- lapply(vocc_by_year, function(vocc) {

vectors <- trim_vector_data(vocc, variable_names, 
  lower_change, upper_change, 
  lower_thresholds, upper_thresholds,
  cell_size = input_cell_size, dist_intercept = dist_intercept,
  max_dist = 120
)
})

@@

trimmed_vector_plots <- lapply(trimmed_vectors, function(vectors) {

try({

  start_time <- vectors$start_time[1]

@@

  vocc_plot <- plot_vocc(vectors,
    vec_aes = "distance",
    min_vec_plotted = input_cell_size,
    NA_label = ".",
    fill_col = "diff",
    fill_label = paste("Change from\n", 
      start_time, "to", start_time + delta_t_total, ""),
    raster_alpha = 1,
    raster_limits = c(raster_min, raster_max),
    white_zero = TRUE,
    vec_alpha = 0.25,
    axis_lables = FALSE,
    transform_col = no_trans 
  ) + ggtitle(climate)
}

@@

  vocc_plot <- plot_vocc(vectors,
    vec_aes = "distance",
    min_vec_plotted = input_cell_size,
    NA_label = ".",
    fill_col = "diff",
    fill_label = paste("Change from\n", 
      start_time, "to", start_time + delta_t_total, ""),
    raster_alpha = 1,
    raster_limits = c(raster_min, raster_max),
    white_zero = TRUE,
    high_fill = "Steel Blue 4",
    low_fill = "Red 3",
    vec_alpha = 0.25,
    axis_lables = FALSE,
    transform_col = no_trans 
  ) + ggtitle(climate)
}

@@

  vocc_plot_temp <- plot_vocc(vectors,
    vec_aes = "distance",
    min_vec_plotted = input_cell_size,
    NA_label = ".",
    fill_col = "temp_diff",
    fill_label = paste("Change from\n", 
      start_time, "to", start_time + delta_t_total, ""),
    raster_alpha = 1,
    raster_limits = c(raster_min_temp, raster_max_temp),
    white_zero = TRUE,
    vec_alpha = 0.25,
    axis_lables = FALSE,
    transform_col = no_trans 
  ) + ggtitle("temperature")

@@

  vocc_plot_do <- plot_vocc(vectors,
    vec_aes = "distance",
    min_vec_plotted = input_cell_size,
    NA_label = ".",
    fill_col = "do_diff",
    fill_label = paste("Change from\n", 
      start_time, "to", start_time + delta_t_total, ""),
    raster_alpha = 1,
    raster_limits = c(raster_min_do, raster_max_do),
    white_zero = TRUE,
    high_fill = "Steel Blue 4",
    low_fill = "Red 3",
    vec_alpha = 0.25,
    axis_lables = FALSE,
    transform_col = no_trans 
  ) + ggtitle("do")

  vocc_plot <- gridExtra::grid.arrange(
    vocc_plot_temp, vocc_plot_do,
    ncol = 2,
    top = grid::textGrob(paste(
      "DO of ", optimal_values[1], "less", min_thresholds[1], 
      "or temperature of ", optimal_values[2], "plus", max_thresholds[2], 
      " over ", start_time, "-", start_time + delta_t_total, ""))
  )
}
vocc_plot
})
})

@@

```{r}
png(
  file = paste0("figs/", spp,
    "/vocc-", min_string, "to", max_string, "-", 
    climate_string, "-", spp, "-", age, "-", ssid_string, "-perc_", biomass_threshold, "-", optimal_string, "-allpairs-test.png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = trimmed_vector_plots,
  ncol = 2,
  top = grid::textGrob(paste("Vectors for cells exceeding", climate, "threshold of", optimal_string, "\n based on", biomass_threshold, "percent of maximum predicted", species, "biomass (", trim_models, ")"), gp=grid::gpar(fontsize=16))
)
dev.off()
```

@@

if (age == "imm") {
  biomass_predictions <- readRDS(paste0(
    "data/", spp, "/all-predictions-", spp, covs, 
    "-imm-biomass-prior-", priors, ".rds"))
}

if (age == "mature") {
  biomass_predictions <- readRDS(paste0(
    "data/", spp, "/all-predictions-", spp, covs, 
    "-mat-biomass-prior-", priors, ".rds"))
}
```

Extract biomass values to match spatial and temporal range of climate vectors
```{r}
#alldata <- lapply(biomass_list, function(biomass_predictions) {

@@

  biomass <- left_join(biomass_change, biomass_covs, by = c("x" = "X", "y"="Y"))

@@

  source_biomass <- left_join(source_cells, biomass, 
    by = c("icell", "x", "y", "start_time")) %>%
    mutate(cell_type = "source") %>% filter(!is.na(start_density))

  # identify all possible control cells have been given a distance == - dist_intercept
  control_cells <- all_vectors %>% filter(distance == (-dist_intercept)) %>% 
    distinct(icell, start_time, .keep_all = TRUE) %>% 
    mutate(distance = (- dist_intercept)) %>% 
    select(-target_X, -target_Y, -target_values, -tid)

  control_biomass <- left_join(control_cells, biomass, 
    by = c("icell", "x", "y", "start_time")) %>%
    mutate(cell_type = "control") %>% filter(!is.na(start_density))

  alldata <- rbind(source_biomass, control_biomass) 
  alldata <- mutate(alldata, treat = ifelse(cell_type=="source", 1, 0)) %>% 
    select(-var_2_min, -var_2_max, -mean_target_X, -mean_target_Y) %>% 
    rename(vect_dist = distance)
  alldata$treat <- as.factor(alldata$treat)

 # alldata
#})
```

@@

```{r}
#rm(vocc_by_sp)
# try({
#   vocc_by_sp <- readRDS(paste0(
#     "data/BACI-", species, "-", age, "-", ssid_string, "-", climate_string, "-", optimal_string, "-", min_string, "to", max_string, "-multiyear-all.rds"
#   ))
# })

#FIXME: should the cells be matched by substrate even when biomass not modelled using substrate?

@@

    alldata <- alldata %>% mutate((!!start_value.st) := 
        arm::rescale(alldata[[start_value]]) )
  #(UQ(rlang::sym(paste0(variable_names[j], "_s")))))
    }

if (!exists("vocc_by_sp")){
# matched <- lapply(alldata, function(alldata) {  
  ## trim non-overlapping values to reduce size of dataset 
  control_min <- quantile(alldata$start_density[alldata$treat=="0"], 0.01)
  source_min <- quantile(alldata$start_density[alldata$treat=="1"], 0.01)
  # control_max <- quantile(alldata$start_density[alldata$treat=="0"], 1)
  # source_max <- quantile(alldata$start_density[alldata$treat=="1"], 1)

  group_min <- max(control_min, source_min)
  # group_max <- min(control_max, source_max)
  alldata <- filter(alldata, start_density >= group_min) 
  #%>% filter(start_density <= group_max)

  # need to be standardized? seems not
  alldata$depth2 <- alldata$depth^2
  alldata$start_density.st <- round(arm::rescale(log(alldata$start_density))*5)/5
  alldata$depth_st <- arm::rescale(log(alldata$depth))
  alldata$depth.st <- round(arm::rescale(log(alldata$depth))*5)/5
  alldata$muddy.st <- arm::rescale(alldata$muddy) 
  alldata$any_rock.st <- arm::rescale(alldata$any_rock)

@@

  # # Using exact match and rounding
  # # Choose data order if not using random
  # alldata <- alldata[(order(alldata$y)), ]
  # if (order == "increasing") alldata <- alldata[rev(order(alldata$start_density)), ]
  # if (order == "decreasing") alldata <- alldata[rev(order(alldata$start_density)), ]
# set.seed(99999)
  matched <- MatchIt::matchit(as.formula(match_formula), 
    exact = c("start_density.st", "start_time"),
    method = "nearest", m.order = "random",
    distance = "probit",
    discard = "both",
    data = alldata)
  # matched
# })
}
```

Print diagnostics for matching
```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
if (!exists("vocc_by_sp")){
match_plots <- plot(matched, interactive = F)
summary(matched)
}

```

Prep matched data for analysis
```{r}
if (!exists("vocc_by_sp")){
#vocc_by_sp <- lapply(matched, function(matched) {    
  mdata <- MatchIt::match.data(matched, distance = "pscore")

  sources <- mdata[row.names(matched$match.matrix), ]
  sources$origobs <- row.names(sources)   
  sources$matchobs <- matched$match.matrix[,1]

  controls <- mdata[matched$match.matrix, ]
  controls$origobs <- row.names(controls)   
  controls$matchobs <- matched$match.matrix[,1]

  mdata <- rbind(sources, controls) %>% tidyr::drop_na() %>% filter(matchobs!="-1")

  matched_time0 <- mdata %>% mutate(after = 0, density = start_density) 
  #%>% dplyr::select(-start_density, -end_density)
  matched_time1 <- mdata %>% mutate(after = 1, density = end_density) 
  #%>% dplyr::select(-start_density, -end_density)

@@

    vocc_by_sp <- mutate(
      vocc_by_sp,
      (!!mean.var) := mean(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE),
      (!!sd.var) := sd(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE),
      (!!std.var) := ((UQ(rlang::sym(paste0(variable_names[j]))) - 
          mean(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE)) / 
          (sd(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE))*2),
      (!!std.var2) := (( UQ(rlang::sym(paste0(variable_names[j]))) - 
          mean(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE) ) / 
          (sd(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE)*2))^2
    )
  }

@@

  # other variable prep
  data$log_density <-  log(data$density)
  data$log_depth <-  log(data$depth)
  data$std_log_depth <- arm::rescale(log(data$depth))
  data$vect_dist2 <- data$vect_dist^2
  data <- mutate(data, time = ifelse(after==1, "end", "begin"))
  data$matchobs <- as.factor(data$matchobs)
  data$origobs  <- as.factor(data$origobs)   
  data$start_time <- as.factor(data$start_time)

#  data
#})
vocc_by_sp <- list()
vocc_by_sp[[1]] <- data
vocc_by_sp[[3]] <- match_formula  
vocc_by_sp[[4]] <- match_plots
saveRDS(vocc_by_sp, file = paste0(
    "data/", spp,
    "/BACI-", spp, "-", age, "-", ssid_string, "-", climate_string, "-", optimal_string, "-", min_string, "to", max_string, "-multiyear-all.rds"
  ))
}
```

## Save spp dataframe
```{r}
#biomass_threshold <- "50"
optimal_string <- paste0(na.omit(trim_thresholds), collapse = "-")
#climate <- "temperature"
try({
  vocc_by_sp <- readRDS(paste0(
    "data/", spp,
    "/BACI-", spp, "-", age, "-", ssid_string, "-", climate_string, "-", optimal_string, "-", min_string, "to", max_string, "-multiyear-all.rds"
  ))
})

n <- nrow(vocc_by_sp[[1]])
species <- rep(species, n) 
mature <- rep(age, n)
ssid <- rep(ssid_string, n)
data <- vocc_by_sp[[1]]
df<- cbind(species, mature, ssid, data)
species <- species[[1]]

@@

if (climate=="temperature") {
dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string))
dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string, age))
}
if (climate=="temperature") {
  saveRDS(df, file = paste0("data/_all/", climate_string,"/", "perc_", biomass_threshold,"/", max_string,"/", age, "/vocc-", climate_string, "-", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"
  ))
}

if (climate=="do") {
  dir.create(file.path("data/_all", climate_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, min_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, min_string, age))  
  }
if (climate=="do") {
  saveRDS(df, file = paste0("data/_all/", climate_string,"/", "perc_", biomass_threshold,"/", min_string,"/", age, "/vocc-", climate_string, "-", min_string, "to", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"
  ))
}

if (climate=="do and temperature") {
  dir.create(file.path("data/_all", climate_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string))  
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, age))  
}

if (climate=="do and temperature") {
  saveRDS(df, file = paste0("data/_all/", climate_string, "/", "perc_", biomass_threshold,"/", age, "/vocc-", climate_string, "-", min_string, "to", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"
  ))
}
```

@@

### Plot matches
```{r}
#FIXME: SAVE PLOTS?

dat_summary <- data %>% 
  group_by(start_time, cell_type) %>%
  tally() %>% filter(cell_type=="source")
data_depth <- data %>% 
  group_by(start_time) %>% 
  mutate(mean_depth = mean(depth))

p1 <- ggplot(data, 
#ggplot(filter(data, as.numeric(matchobs) <= 550), 
  aes(y=Y, x=X, shape=as.factor(treat), colour=as.factor(matchobs))) +
  geom_point(alpha=0.8, size = 1) +
  scale_shape_manual(values= c(0, 15)) +
  scale_colour_viridis_d(option="C", guide = FALSE) +
  facet_wrap(~start_time) +
  theme_bw()
p1

lapply(variable_names, function(j) {
ggplot(data, aes(y=log_density, x=UQ(rlang::sym(paste(j))), colour=time)) +
  geom_point(alpha=0.35) +
  scale_colour_viridis_d(option="C") +
  facet_grid(start_time~cell_type) +
  theme_bw()
})

p2 <- ggplot(data, aes(std_log_depth, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_wrap(~start_time) +
  theme_bw()
p2

@@

p3 <- ggplot(data, aes(log_density, fill = cell_type)) +
  geom_density(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  facet_grid(start_time~time, scales = 'fixed') +
  theme_bw() + theme(legend.position='none')
p3

p4 <- ggplot(data, aes(log_density, fill = cell_type)) +
  geom_histogram(alpha=0.45) +
  scale_fill_viridis_d(option="C") +
  facet_grid(time~start_time) +
  theme_bw() + theme(legend.position='none')
p4

dat_summary <- data %>% 
  group_by(start_time, cell_type) %>% 
  tally() %>% filter(cell_type=="source")

p5 <- ggplot(data, aes(y=log_density, x=cell_type, fill=cell_type)) +
  geom_boxplot(alpha=0.5) +
  scale_fill_viridis_d(option="C") +
  geom_text(data = dat_summary,
            aes(cell_type, min(data$log_density)+1, label = n), hjust = 1.25) +
  facet_grid(time~start_time) +
  theme_bw() + theme(legend.position='none')
p5
```

>>>>

#### Set default cell sizes and scale
```{r, echo=FALSE}
input_cell_size <- 2
dist_intercept <- input_cell_size / 2
scale_fac <- 1
delta_t_step <- 2
skip_time <- NULL
```

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
if (region == "both odd year surveys") {
  survey <- c("SYN QCS", "SYN HS")
  model_ssid <- c(1, 3)
  ssid_string <- paste0(model_ssid, collapse = "n")
  start_years <- list("2009" = 2009, "2011" = 2011, "2013" = 2013, "2015" = 2015)
  # maybe remove 2011 & 2015 once we can add "2017"=2017 to avoid start and end values overlapping
  years <- NULL
}

if (region == "West Coast Vancouver Island") {
  survey <- c("SYN WCVI")
  model_ssid <- c(4)
  ssid_string <- paste0(model_ssid, collapse = "n")
  start_years <- list("2008" = 2008, "2010" = 2010, "2012" = 2012, "2014" = 2014, "2016" = 2016)
  # prob need to remove 2010 & 2014
  years <- NULL
}

if (region == "West Coast Haida Gwaii") {
  survey <- c("SYN WCHG")
  model_ssid <- c(16)
  ssid_string <- paste0(model_ssid, collapse = "n")
  start_years <- list("2008" = 2008, "2010" = 2010, "2012" = 2012, "2014" = 2014, "2016" = 2016)
  # prob need to remove 2010 & 2014
  years <- NULL
}
```

@@

if (climate == "temperature") {
  temp_threshold <- params$threshold

@@

  upper_thresholds <- round(.upper[1], digits = 2)
  if (is.na(upper_thresholds)) {
    stop(print("Temp maximum not modelled"))
  }

@@

  .lower <- na.omit(.lower)
  lower_thresholds <- round(.lower[1], digits = 2)
  if (is.na(lower_thresholds)) {
    stop(print("DO minimum not modelled"))
  }
  lower_model <- root_params[rev(order(root_params$do_maxy)), ]$model

@@

# Calculate climate vectors
```{r}
vocc_by_year <- lapply(start_years, function(start_time) {
  try({
    vocc <- readRDS(paste0(
      "data/vocc-", ssid_string, "-", climate_string, "-",
      min_string, "to", max_string, "-", start_time, "-", delta_t_total, ".rds"
    ))
  })

@@

### Filter vectors to match optimal range for chosen species
```{r}
trimmed_vectors <- lapply(vocc_by_year, function(vocc) {
  vectors <- trim_vector_data(vocc, variable_names,
    lower_change, upper_change,
    lower_thresholds, upper_thresholds,
    cell_size = input_cell_size, dist_intercept = dist_intercept,
    max_dist = 120
  )
})

@@

trimmed_vector_plots <- lapply(trimmed_vectors, function(vectors) {
  try({
    start_time <- vectors$start_time[1]

@@

      vocc_plot <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        white_zero = TRUE,
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min, raster_max),
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle(climate)
    }

@@

      vocc_plot_temp <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "temp_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_temp, raster_max_temp),
        white_zero = TRUE,
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("temperature")

@@

      vocc_plot_do <- plot_vocc(vectors,
        vec_aes = "distance",
        min_vec_plotted = input_cell_size,
        NA_label = ".",
        fill_col = "do_diff",
        fill_label = paste(
          "Change from\n",
          start_time, "to", start_time + delta_t_total, ""
        ),
        raster_alpha = 1,
        raster_limits = c(raster_min_do, raster_max_do),
        white_zero = TRUE,
        high_fill = "Steel Blue 4",
        low_fill = "Red 3",
        vec_alpha = 0.25,
        axis_lables = FALSE,
        transform_col = no_trans
      ) + ggtitle("do")

      vocc_plot <- gridExtra::grid.arrange(
        vocc_plot_temp, vocc_plot_do,
        ncol = 2,
        top = grid::textGrob(paste(
          "DO of ", optimal_values[1], "less", min_thresholds[1],
          "or temperature of ", optimal_values[2], "plus", max_thresholds[2],
          " over ", start_time, "-", start_time + delta_t_total, ""
        ))
      )
    }
    vocc_plot
  })
})

@@

```{r}
png(
  file = paste0(
    "figs/", spp,
    "/vocc-", min_string, "to", max_string, "-",
    climate_string, "-", spp, "-", age, "-", ssid_string, "-perc_", biomass_threshold, "-", optimal_string, "-allpairs-test.png"
  ),
  res = 600,
  units = "in",
  width = 8.5,
  height = 11
)
gridExtra::grid.arrange(
  grobs = trimmed_vector_plots,
  ncol = 2,
  top = grid::textGrob(paste("Vectors for cells exceeding", climate, "threshold of", optimal_string, "\n based on", biomass_threshold, "percent of maximum predicted", species, "biomass (", trim_models, ")"), gp = grid::gpar(fontsize = 16))
)
dev.off()
```

@@

if (age == "imm") {
  biomass_predictions <- readRDS(paste0(
    "data/", spp, "/all-predictions-", spp, covs,
    "-imm-biomass-prior-", priors, ".rds"
  ))
}

if (age == "mature") {
  biomass_predictions <- readRDS(paste0(
    "data/", spp, "/all-predictions-", spp, covs,
    "-mat-biomass-prior-", priors, ".rds"
  ))
}
```

Extract biomass values to match spatial and temporal range of climate vectors
```{r}
# alldata <- lapply(biomass_list, function(biomass_predictions) {

@@

biomass <- left_join(biomass_change, biomass_covs, by = c("x" = "X", "y" = "Y"))

@@

source_biomass <- left_join(source_cells, biomass,
  by = c("icell", "x", "y", "start_time")
) %>%
  mutate(cell_type = "source") %>%
  filter(!is.na(start_density))

# identify all possible control cells have been given a distance == - dist_intercept
control_cells <- all_vectors %>%
  filter(distance == (-dist_intercept)) %>%
  distinct(icell, start_time, .keep_all = TRUE) %>%
  mutate(distance = (-dist_intercept)) %>%
  select(-target_X, -target_Y, -target_values, -tid)

control_biomass <- left_join(control_cells, biomass,
  by = c("icell", "x", "y", "start_time")
) %>%
  mutate(cell_type = "control") %>%
  filter(!is.na(start_density))

alldata <- rbind(source_biomass, control_biomass)
alldata <- mutate(alldata, treat = ifelse(cell_type == "source", 1, 0)) %>%
  select(-var_2_min, -var_2_max, -mean_target_X, -mean_target_Y) %>%
  rename(vect_dist = distance)
alldata$treat <- as.factor(alldata$treat)

# alldata
# })
```

@@

```{r}
# rm(vocc_by_sp)
# try({
#   vocc_by_sp <- readRDS(paste0(
#     "data/BACI-", species, "-", age, "-", ssid_string, "-", climate_string, "-", optimal_string, "-", min_string, "to", max_string, "-multiyear-all.rds"
#   ))
# })

# FIXME: should the cells be matched by substrate even when biomass not modelled using substrate?

@@

  alldata <- alldata %>% mutate((!!start_value.st) :=
    arm::rescale(alldata[[start_value]]))
  # (UQ(rlang::sym(paste0(variable_names[j], "_s")))))
}

if (!exists("vocc_by_sp")) {
  # matched <- lapply(alldata, function(alldata) {
  ## trim non-overlapping values to reduce size of dataset
  control_min <- quantile(alldata$start_density[alldata$treat == "0"], 0.01)
  source_min <- quantile(alldata$start_density[alldata$treat == "1"], 0.01)
  # control_max <- quantile(alldata$start_density[alldata$treat=="0"], 1)
  # source_max <- quantile(alldata$start_density[alldata$treat=="1"], 1)

  group_min <- max(control_min, source_min)
  # group_max <- min(control_max, source_max)
  alldata <- filter(alldata, start_density >= group_min)
  # %>% filter(start_density <= group_max)

  # need to be standardized? seems not
  alldata$depth2 <- alldata$depth^2
  alldata$start_density.st <- round(arm::rescale(log(alldata$start_density)) * 5) / 5
  alldata$depth_st <- arm::rescale(log(alldata$depth))
  alldata$depth.st <- round(arm::rescale(log(alldata$depth)) * 5) / 5
  alldata$muddy.st <- arm::rescale(alldata$muddy)
  alldata$any_rock.st <- arm::rescale(alldata$any_rock)

@@

  # # Using exact match and rounding
  # # Choose data order if not using random
  # alldata <- alldata[(order(alldata$y)), ]
  # if (order == "increasing") alldata <- alldata[rev(order(alldata$start_density)), ]
  # if (order == "decreasing") alldata <- alldata[rev(order(alldata$start_density)), ]
  # set.seed(99999)
  matched <- MatchIt::matchit(as.formula(match_formula),
    exact = c("start_density.st", "start_time"),
    method = "nearest", m.order = "random",
    distance = "probit",
    discard = "both",
    data = alldata
  )
  # matched
  # })
}
```

Print diagnostics for matching
```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
if (!exists("vocc_by_sp")) {
  match_plots <- plot(matched, interactive = F)
  summary(matched)
}
```

Prep matched data for analysis
```{r}
if (!exists("vocc_by_sp")) {
  # vocc_by_sp <- lapply(matched, function(matched) {
  mdata <- MatchIt::match.data(matched, distance = "pscore")

  sources <- mdata[row.names(matched$match.matrix), ]
  sources$origobs <- row.names(sources)
  sources$matchobs <- matched$match.matrix[, 1]

  controls <- mdata[matched$match.matrix, ]
  controls$origobs <- row.names(controls)
  controls$matchobs <- matched$match.matrix[, 1]

  mdata <- rbind(sources, controls) %>%
    tidyr::drop_na() %>%
    filter(matchobs != "-1")

  matched_time0 <- mdata %>% mutate(after = 0, density = start_density)
  # %>% dplyr::select(-start_density, -end_density)
  matched_time1 <- mdata %>% mutate(after = 1, density = end_density)
  # %>% dplyr::select(-start_density, -end_density)

@@

    vocc_by_sp <- mutate(
      vocc_by_sp,
      (!!mean.var) := mean(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE),
      (!!sd.var) := sd(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE),
      (!!std.var) := ((UQ(rlang::sym(paste0(variable_names[j]))) -
        mean(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE)) /
        (sd(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE)) * 2),
      (!!std.var2) := ((UQ(rlang::sym(paste0(variable_names[j]))) -
        mean(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE)) /
        (sd(UQ(rlang::sym(paste0(variable_names[j]))), na.rm = TRUE) * 2))^2
    )
  }

@@

  # other variable prep
  data$log_density <- log(data$density)
  data$log_depth <- log(data$depth)
  data$std_log_depth <- arm::rescale(log(data$depth))
  data$vect_dist2 <- data$vect_dist^2
  data <- mutate(data, time = ifelse(after == 1, "end", "begin"))
  data$matchobs <- as.factor(data$matchobs)
  data$origobs <- as.factor(data$origobs)
  data$start_time <- as.factor(data$start_time)

  #  data
  # })
  vocc_by_sp <- list()
  vocc_by_sp[[1]] <- data
  vocc_by_sp[[3]] <- match_formula
  vocc_by_sp[[4]] <- match_plots
  saveRDS(vocc_by_sp, file = paste0(
    "data/", spp,
    "/BACI-", spp, "-", age, "-", ssid_string, "-", climate_string, "-", optimal_string, "-", min_string, "to", max_string, "-multiyear-all.rds"
  ))
}
```

## Save spp dataframe
```{r}
# biomass_threshold <- "50"
optimal_string <- paste0(na.omit(trim_thresholds), collapse = "-")
# climate <- "temperature"
try({
  vocc_by_sp <- readRDS(paste0(
    "data/", spp,
    "/BACI-", spp, "-", age, "-", ssid_string, "-", climate_string, "-", optimal_string, "-", min_string, "to", max_string, "-multiyear-all.rds"
  ))
})

n <- nrow(vocc_by_sp[[1]])
species <- rep(species, n)
mature <- rep(age, n)
ssid <- rep(ssid_string, n)
data <- vocc_by_sp[[1]]
df <- cbind(species, mature, ssid, data)
species <- species[[1]]

@@

if (climate == "temperature") {
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, max_string, age))
}
if (climate == "temperature") {
  saveRDS(df, file = paste0("data/_all/", climate_string, "/", "perc_", biomass_threshold, "/", max_string, "/", age, "/vocc-", climate_string, "-", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"))
}

if (climate == "do") {
  dir.create(file.path("data/_all", climate_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, min_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, min_string, age))
}
if (climate == "do") {
  saveRDS(df, file = paste0("data/_all/", climate_string, "/", "perc_", biomass_threshold, "/", min_string, "/", age, "/vocc-", climate_string, "-", min_string, "to", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"))
}

if (climate == "do and temperature") {
  dir.create(file.path("data/_all", climate_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string))
  dir.create(file.path("data/_all", climate_string, biomass_threshold_string, age))
}

if (climate == "do and temperature") {
  saveRDS(df, file = paste0("data/_all/", climate_string, "/", "perc_", biomass_threshold, "/", age, "/vocc-", climate_string, "-", min_string, "to", max_string, "-", spp, "-", age, "-", optimal_string, "-", ssid_string, "-all.rds"))
}
```

@@

### Plot matches
```{r}
# FIXME: SAVE PLOTS?

dat_summary <- data %>%
  group_by(start_time, cell_type) %>%
  tally() %>%
  filter(cell_type == "source")
data_depth <- data %>%
  group_by(start_time) %>%
  mutate(mean_depth = mean(depth))

p1 <- ggplot(
  data,
  # ggplot(filter(data, as.numeric(matchobs) <= 550),
  aes(y = Y, x = X, shape = as.factor(treat), colour = as.factor(matchobs))
) +
  geom_point(alpha = 0.8, size = 1) +
  scale_shape_manual(values = c(0, 15)) +
  scale_colour_viridis_d(option = "C", guide = FALSE) +
  facet_wrap(~start_time) +
  theme_bw()
p1

lapply(variable_names, function(j) {
  ggplot(data, aes(y = log_density, x = UQ(rlang::sym(paste(j))), colour = time)) +
    geom_point(alpha = 0.35) +
    scale_colour_viridis_d(option = "C") +
    facet_grid(start_time ~ cell_type) +
    theme_bw()
})

p2 <- ggplot(data, aes(std_log_depth, fill = cell_type)) +
  geom_density(alpha = 0.5) +
  scale_fill_viridis_d(option = "C") +
  facet_wrap(~start_time) +
  theme_bw()
p2

@@

p3 <- ggplot(data, aes(log_density, fill = cell_type)) +
  geom_density(alpha = 0.5) +
  scale_fill_viridis_d(option = "C") +
  facet_grid(start_time ~ time, scales = "fixed") +
  theme_bw() + theme(legend.position = "none")
p3

p4 <- ggplot(data, aes(log_density, fill = cell_type)) +
  geom_histogram(alpha = 0.45) +
  scale_fill_viridis_d(option = "C") +
  facet_grid(time ~ start_time) +
  theme_bw() + theme(legend.position = "none")
p4

dat_summary <- data %>%
  group_by(start_time, cell_type) %>%
  tally() %>%
  filter(cell_type == "source")

p5 <- ggplot(data, aes(y = log_density, x = cell_type, fill = cell_type)) +
  geom_boxplot(alpha = 0.5) +
  scale_fill_viridis_d(option = "C") +
  geom_text(
    data = dat_summary,
    aes(cell_type, min(data$log_density) + 1, label = n), hjust = 1.25
  ) +
  facet_grid(time ~ start_time) +
  theme_bw() + theme(legend.position = "none")
p5
```
